### 2017-05-29 doc/related.tex
related work updated

\namecite{li2015convergent} train a Convolutional Neural Networks (CNN)
with different random initializations
%based on the architecture introduced in \cite{krizhevsky2012imagenet} 
on the ImageNet dataset \cite{krizhevsky2012imagenet}. For each layer
in all networks they store the activation values produced on the
validation set of ILSVRC and align similar neurons of different
networks. They conclude that while some features are learned across
networks, some seem to depend on the initialization. Other works on
visualizing the role of individual hidden units in deep models for vision
synthesize images by optimizing random images through backpropagation
to maximize the activity of units
\cite{erhan2009visualizing,simonyan2013deep,yosinski2015understanding,nguyen2016multifaceted}
or to approximate the activation vectors of particular layers
\cite{mahendran2015visualizing,dosovitskiy2015inverting}.

>>>>

\namecite{li2015convergent} use a Convolutional Neural Networks (CNN)
based on the architecture of \namecite{krizhevsky2012imagenet}, 
and train it on the ImageNet dataset using different random initializations. For each layer
in all networks they store the activation values produced on the
validation set of ILSVRC and align similar neurons of different
networks. They conclude that while some features are learned across
networks, some seem to depend on the initialization. Other works on
visualizing the role of individual hidden units in deep models for vision
synthesize images by optimizing random images through backpropagation
to maximize the activity of units
\cite{erhan2009visualizing,simonyan2013deep,yosinski2015understanding,nguyen2016multifaceted}
or to approximate the activation vectors of particular layers
\cite{mahendran2015visualizing,dosovitskiy2015inverting}.

While this paper was under review, a number of articles appeared which also 
investigate linguistic representations in LSTM architectures. In an 
approach similar to ours, \namecite{li2016understanding} study the contribution of 
individual input tokens as well as hidden units and word embedding dimensions 
by erasing them from the representation and analyzing how this affects the model.
\namecite{adi2016fine} take an alternative approach by introducing prediction tasks 
to analyze information encoded in sentence embeddings about sentence length, 
sentence content and word order. Finally, \namecite{linzen2016assessing} examine 
the acquisition of long-distance dependencies through the study of number agreement 
in different variations of an LSTM model with different objectives (number prediction, 
grammaticality judgment, and language modeling). Their results show that such dependencies 
can be captured with very high accuracy when the model receives a strong supervision 
signal (that is, whether the subject is plural or singular), but simple language models still capture 
the majority of test cases. All these models focus on text-based tasks and do not take other 
modalities such as visual input into account.
